\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{enumitem}

% Add custom section formatting
\makeatletter
\renewcommand\section{\@startsection{section}{1}{0pt}%
  {0.5ex}% space before
  {0.5ex}% space after
  {\normalsize\bfseries}}% style
\makeatother

\begin{document}
\pagenumbering{gobble}

\begin{center}
{\Large \textbf{Shaan Fulton}}\\
Berkeley, CA $\vert$ shaanfulton@berkeley.edu $\vert$ (650) 714 7406 $\vert$ linkedin.com/in/shaanf
\end{center}


\section*{EDUCATION}
\vspace{2mm}
\hrule
\vspace{4mm}
\noindent\textbf{University of California, Berkeley} \hfill May 2026\\
\textit{Bachelor of Arts in Computer Science and Economics} \hfill GPA: 4.0
\vspace{2mm}


\section*{TECHNICAL SKILLS}
\vspace{2mm}
\hrule
\vspace{4mm}
\noindent\textbf{Languages:} Typescript, CSS, SQL, Python, Java, R, Swift\\
\textbf{DevOps:} AWS CDK, ECS, EC2, Kubernetes, Docker compose, GitHub Actions, Git\\
\textbf{Databases:} PostgreSQL, MongoDB\\
\textbf{Tools:} Figma, Adobe Illustrator, Google Ads, Google Analytics
\vspace{2mm}


\section*{WORK EXPERIENCE}
\vspace{2mm}
\hrule
\vspace{4mm}
\noindent\textbf{TELO Trucks} \hfill San Carlos, CA\\
\textit{Web Development Lead} \hfill May 2024 - Present
\begin{itemize}[itemsep=0pt]
\item Architected, designed, and deployed a scalable pre-order website increasing vehicle pre-orders from \$5M to \$25M per month and handling up to 170,000 daily users using Next.js, Express, and PostgreSQL.
\item Implemented infrastructure as code using AWS CDK and Docker to orchestrate CI/CD pipeline on website database and server ECS clusters saving company 50+ dev hours per month.
\item Automated database migration by developing Python ETL scripts, successfully migrating 10K records from archived CSV to PostgreSQL with zero downtime.
\item Implemented Sentry logging and AWS cloudwatch alerts to capture and resolve 100+ code issues, reducing monthly site-related customer complaints by 99\%.
\item Implemented custom Express CMS with MongoDB, to create automated press releases and blog posts, saving 20+ marketing team hours per month.
\end{itemize}

\noindent\textbf{Jerry's Club} \hfill Berkeley, CA\\
\textit{Co-Founder and Software Lead} \hfill January 2024 - Present
\begin{itemize}[itemsep=0pt]
\item Leading software team in developing marketplace app built on React Native and Django REST framework.
\item Developed intelligent RAG system using local Llama 3 for dynamic query generation and semantic search across PostgreSQL pricing data, feeding contextualized results to OpenAI API to achieve industry-leading 99\% accuracy on product price valuations, generated up to 10x faster than recommerce competitors.
\item Mentored by Tesla co-founder Marc Tarpenning on product and technical strategy.
\end{itemize}

\noindent\textbf{Jump Robotics} \hfill Palo Alto, CA\\
\textit{Co-Founder and Software Lead} \hfill August 2019 - May 2023
\begin{itemize}[itemsep=0pt]
\item Architected team structure and task management for 20-member robotics engineering organization, implementing Git workflows and agile methodologies across 3 sub-teams.
\item Optimized Google Ads campaigns with Google Analytics and modular Next.js landing pages to A/B test donation routes, achieving \$150K in annual monetary contributions as well as \$100K in-kind.
\item Developed robot control systems in Java, implementing custom PID design to control swerve-drive drivetrain, increasing reliability from 50\% to 100\% and resulting in winning the FRC Design Award (among 3,500+ competing global teams).
\end{itemize}

\noindent\textbf{OpsCruise} \hfill Sunnyvale, CA\\
\textit{Software Developer} \hfill June 2019 - December 2021
\begin{itemize}[itemsep=0pt]
\item Designed and developed high-conversion website for Kubernetes observability startup using React and TypeScript, contributing to successful acquisition by Virtana at \$30M valuation.
\item Collaborated with marketing team to A/B test landing pages, resulting in enterprise demo requests by Tesla, Comcast, and other Fortune 500 companies generated directly through the website.
\end{itemize}

\end{document}
